RNA-seq from 4 cell populations

### 2021-11-01 deconvolution/fans4/molec_profiling.Rmd
add per cell type analysis

### Save processed data
```{r save.processed}
storeData( geneCounts, "geneCounts_merged.RDS", "Merged gene counts for Mol Prof data")
storeData( info, "info_merged.RDS", "Merge metadata for Mol Prof data")
```

# Per cell type analysus
```{r preprocess.CT}
ALL_USED_IDs= unique(c('syn22321012', 'syn22321013', 'syn22321014', 'syn22321016', 'syn2232101', 'syn26000845','syn25976117', 'syn25976127', 'syn22321013', 'syn22321014', 'syn22321016', 'syn26000850', 'syn25976122', 'syn25976136'))

>>>>

### Save processed data
```{r save.processed}
ALL_USED_IDs= unique(c('syn22321012', 'syn22321013', 'syn22321014', 'syn22321016', 'syn2232101', 'syn26000845','syn25976117', 'syn25976127', 'syn22321013', 'syn22321014', 'syn22321016', 'syn26000850', 'syn25976122', 'syn25976136'))

storeData( geneCounts, "geneCounts_merged.RDS", "Merged gene counts for Mol Prof data")
storeData( info, "info_merged.RDS", "Merge metadata for Mol Prof data")
```

# Per cell type analysus
```{r preprocess.CT}
